Cooperative Decision Making for Communities of Autonomous Web Services

### 2013-12-11 proposal/presentation/ekpresentation/ehsan_presentation.tex
changes

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
        \item Contribution and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}

>>>>

\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Solution Concepts: Shapley Value}
    \begin{definition} [Marginal contribution]\label{dfn:marginalcontribution}
        The {\color{red}marginal contribution} of agent $i$ for a coalition $C \subseteq N \backslash \{i\}$ is $mc_i(C) = v(C \cup \{i\}) - v(C)$
    \end{definition}

    \begin{itemize}
        \item By considering average marginal contribution over all possible subset of coalitions, we can achieve a fair distribution.\\
        \item Let $\prod(N)$ denote the set of all permutations of the sequence $(1,...n)$. Therefore: $\phi_i(N,v) = \frac{\sum_{\sigma \in \phi_i(N)}}{mc(\sigma)}$
    \end{itemize}

    \begin{definition} [Shapley Value]\label{dfn:shapleyvalue}
        Given a coalitional game $(N,v)$, the Shapley value of player $i$ is given by: \\
        $\phi_i(N,v) = \sum_{S \subseteq N \backslash \left\{i\right\} } \frac{|S|! (|N|-|S|-1)!}{|N|!} (v(S \cup \left\{i\right\}) - v(S))$
    \end{definition}
\end{frame}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}{Some properties}
    \begin{itemize}
        \item The core may not always be non-empty
        \item Shapley value always exists and is unique.
        \item When the valuation function is {\color{red}superadditive}, the Shapley value is {\color{red}individually rational}, i.e., it is an imputation.
        \item When the valuation function is {\color{red}convex}, the Shapley value is also group rational, hence, it is in the {\color{red}core}.        
        \item A convex game has a non-empty core
        \item There are other well-known solution concepts: The bargaining set, The nucleolus and The nucleolus.
    \end{itemize}
\end{frame}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Proposed Research}
\begin{frame}{Presentation Outline}
    \begin{itemize}
     	\itemsep=.5cm
    	\item Introduction
    	\item Background and Literature Review
    	\item {\bf Proposed Research}
        \item Contribution and Research Activities
    	\item Time Line
    \end{itemize}
\end{frame}
